Berkeley Police Stop Data Maps

### 2016-08-02 Rebeccas_location_Code2/StopData_Maps.Rmd
map changes

berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 14)
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, color = Incident.Type), data = mergedf, alpha = 0.2, size = 3) + 
  scale_colour_discrete( "Incident Type", labels = c("Pedestrian Stop", "Bicycle Stop", "Suspicious Vehicle Stop",  "Traffic Stop" ) ) +
  theme ( 
		#legend.position = c(0.05, 0.05), # put the legend INSIDE the plot area
		#legend.justification = c(0, 0),
		#legend.background = element_rect(colour = F, fill = "white"),
		#legend.key = element_rect (fill = F, colour = F),
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stops by Incident Type, 2015-2016") 
```

## MAP 2.1
```{r}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, size = CarSearch, color = Race), data = mergedf, alpha = 0.2) + 
  scale_size_discrete( "Car Search", labels = c("No Search", "Search") ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stop Car Searches by Race 2015-2016") +
  facet_wrap(~ Race, ncol = 3 ) 
```

@@

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race), data = df, alpha = 0.5, size = 6) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stops: Emergency Psch Evaluation, by Race 2015-2016")

@@

## MAP 3:
```{r}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = factor(Gender)), data = mergedf, alpha = 0.2, size = 3) + 
  scale_colour_discrete( "Gender", labels = c("Female", "Male") ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stops by Gender, 2015-2016") 
```

@@

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race, size= Arrest), data = df, alpha = 0.5) + 
  scale_size_discrete( range = c(7, 3) ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Traffic Stops Only, by Race 2015-2016") +
  facet_grid(~ Race)
```

@@

## MAP 9
```{r, fig.height = 25, fig.width = 5}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "StopDensity",
    low = "white", mid = "orange", high = "red", midpoint = 100) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap( ~ Race ) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Race") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

## MAP 10 : AgeRange Density Facet
```{r, fig.height = 25, fig.width = 5}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "Stop Density",
    low = "white", mid = "orange", high = "red", midpoint = 25) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap(~ AgeRange) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Age Range") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

## MAP 11: By Race Again
```{r, fig.height = 25, fig.width = 5}
# ggmap(berkMap) +
# geom_point(aes(x = long, y = lat, colour = Race, size = Race),
#   data = mergedf)

@@

## Population by census block group:
```{r}
shpfile <- "Census_tracts_2010.shp"
sh <- readShapePoly("C:/Users/Rebecca/Dropbox/School/2016_su_School/stat133/finalproject_angry_ladies/Rebeccas_location_Code2/Census_Tract_Polygons2010/Census_tracts_2010.shp")
plot(sh)
sh@data$ID <- as.numeric(sh@data$ID)

# Read in the demographic data and merge on Neighbourhood Id
demo <- read.csv(file="Census_tracts_2010.csv", header=T)
sh2 <- merge(sh, demo, by='ID')

@@

# Map 15
```{r}
j <- merge( b3, demo, by = "group"  )

# Plot
bMap12 <- ggmap(berkMap) +
  geom_polygon(aes(x=long,y=lat, group=group, fill=TotalPop), data=j, color='white') +
  scale_fill_gradient(low='white', high='orange') +
  geom_point( data = mergedf, aes(x = long, y = lat), alpha = 0.2, size = 3, color = 'red' )
bMap12
```

>>>>

berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 14)
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, color = Incident.Type), data = mergedf, alpha = 0.2, size = 3) + 
  scale_colour_discrete( "Incident Type", labels = c("Pedestrian Stop", "Bicycle Stop", "Suspicious Vehicle Stop",  "Traffic Stop" ) ) +
  theme ( 
		#legend.position = c(0.05, 0.05), # put the legend INSIDE the plot area
		#legend.justification = c(0, 0),
		#legend.background = element_rect(colour = F, fill = "white"),
		#legend.key = element_rect (fill = F, colour = F),
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("All BPD Stops by Incident Type, 2015-2016") 
```

## MAP 2.1
```{r}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, size = CarSearch, color = Race), data = mergedf, alpha = 0.2) + 
  scale_size_discrete( "Car Search", labels = c("No Search", "Search") ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD All Stops w/ Car Searches by Race 2015-2016") +
  facet_wrap(~ Race, ncol = 3 ) 
```

@@

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race), data = df, alpha = 0.5, size = 6) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Stops with Emergency Psch Evaluation, by Race 2015-2016")

@@

## MAP 3:
```{r}
ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = factor(Gender)), data = mergedf, alpha = 0.2, size = 3) + 
  scale_colour_discrete( "Gender", labels = c("Female", "Male") ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("All BPD Stops by Gender, 2015-2016") 
```

@@

ggmap(berkMap) +
  geom_point(aes(x = long, y = lat, colour = Race, size= Arrest), data = df, alpha = 0.5) + 
  scale_size_discrete( range = c(5, 2) ) +
  theme ( 
		panel.grid.major = element_blank (), # remove major grid
		panel.grid.minor = element_blank (),  # remove minor grid
		axis.text = element_blank (), 
		axis.title = element_blank (),
		axis.ticks = element_blank ()
		) + 
  ggtitle("BPD Traffic Stops Only, by Race 2015-2016") +
  facet_grid(~ Race)
```

@@

## MAP 9
```{r}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "StopDensity",
    low = "white", mid = "orange", high = "red", midpoint = 100) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap( ~ Race ) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Race") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

## MAP 10 : AgeRange Density Facet
```{r}
ggmap(berkMap) +
  stat_density2d( aes(x = long, y = lat, fill = ..level.., alpha = ..level..),
    bins = I(5), geom = "polygon", data = mergedf ) +
  scale_fill_gradient2( "Stop Density",
    low = "white", mid = "orange", high = "red", midpoint = 25) +
  labs(x = "Longitude", y = "Latitude") + facet_wrap(~ AgeRange) +
  scale_alpha(range = c(.2, .55), guide = FALSE) +
  ggtitle("BPD Stop Contour Map of Berkeley by Age Range") +
  guides(fill = guide_colorbar(barwidth = 1.5, barheight = 10))
```

## MAP 11: By Race Again
```{r}
# ggmap(berkMap) +
# geom_point(aes(x = long, y = lat, colour = Race, size = Race),
#   data = mergedf)

@@

## Population by census block group:
```{r}
shpfile <- "Census_tracts_2010.shp"
sh <- readShapePoly("Census_Tract_Polygons2010/Census_tracts_2010.shp")
plot(sh)
sh@data$ID <- as.numeric(sh@data$ID)

# Read in the demographic data and merge on Neighbourhood Id
demo <- read.csv(file="Census_tracts_2010.csv", header = TRUE)
sh2 <- merge(sh, demo, by='ID')

@@

<!-- # Map 15 -->
<!-- ```{r} -->
<!-- sh2data <- sh2@data -->
<!-- j <- merge( sh2data, demo, by.x= "GEOID10.x", by.y="GEOID10"  ) -->

<!-- # Plot -->
<!-- bMap12 <- ggmap(berkMap) + -->
<!--   geom_polygon(aes(x=long,y=lat, group=group, fill=TotalPop), data=sh2, color='white') + -->
<!--   scale_fill_gradient(low='white', high='orange') + -->
<!--   geom_point( data = mergedf, aes(x = long, y = lat), alpha = 0.2, size = 3, color = 'red' ) -->
<!-- bMap12 -->
<!-- ``` -->
